A conditional permutation-based approach to test confounder and center effects in machine learning models

### 2021-10-21 simulated/normality_and_linearity_violation.tex
example notebook

\begin{figure}
\centering
\includegraphics{normality_and_linearity_violation_files/normality_and_linearity_violation_3_0.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{normality_and_linearity_violation_files/normality_and_linearity_violation_3_1.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{normality_and_linearity_violation_files/normality_and_linearity_violation_3_2.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{normality_and_linearity_violation_files/normality_and_linearity_violation_3_3.png}
\caption{png}
\end{figure}

@@

\begin{lstlisting}[language=Python]
model = Ridge(alpha=0)
model.fit(y=y, X=X)
yhat = model.predict(X)
sns.scatterplot(x=y, y=yhat, alpha=0.3)
#sns.lineplot(x=y, y=y, linestyle="--")
model.coef_
\end{lstlisting}

@@

\begin{figure}
\centering
\includegraphics{normality_and_linearity_violation_files/normality_and_linearity_violation_5_1.png}
\caption{png}
\end{figure}

@@

\begin{lstlisting}[language=Python]
model = Ridge(alpha=2000)
model.fit(y=y, X=X)
yhat = model.predict(X)
sns.scatterplot(x=y, y=yhat, alpha=0.3)
#sns.lineplot(x=y, y=y, linestyle="--")
model.coef_
\end{lstlisting}

@@

\begin{figure}
\centering
\includegraphics{normality_and_linearity_violation_files/normality_and_linearity_violation_7_1.png}
\caption{png}
\end{figure}

\begin{lstlisting}[language=Python]
\end{lstlisting}

>>>>

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_0.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_1.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_2.png}
\caption{png}
\end{figure}

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_3_3.png}
\caption{png}
\end{figure}

@@

\begin{lstlisting}[language=Python]
model = Ridge(alpha=0)
model.fit(y=y, X=X)
yhat = model.predict(X)
sns.scatterplot(x=y, y=yhat, alpha=0.3)
model.coef_
\end{lstlisting}

@@

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_5_1.png}
\caption{png}
\end{figure}

@@

\begin{lstlisting}[language=Python]
model = Ridge(alpha=2000)
model.fit(y=y, X=X)
yhat = model.predict(X)
sns.scatterplot(x=y, y=yhat, alpha=0.3)
model.coef_

\end{lstlisting}

@@

\begin{figure}
\centering
\includegraphics{fig/normality_and_linearity_violation_files/normality_and_linearity_violation_7_1.png}
\caption{png}
\end{figure}
